	\begin{longtable}{p{4.5cm}p{10.5cm}}
		\toprule
		\multicolumn{1}{c}{{\textbf{Section} \texttt{singletop}}} & \multicolumn{1}{c}{{\textbf{Description}}} \\ 
		\midrule
		\texttt{c\_phiq} & Sets real Wilson coefficient of $\Qone$ for processes 164 and 169. See \cref{subsec:offstop} 
		and ref.~\cite{Neumann:2019kvk}. \\
		\texttt{c\_phiphi} & Sets real and imaginary part of the $\Qtwo$ Wilson coefficient. \\
		\texttt{c\_tw} & Sets real and imaginary part of the $\Qthree$ Wilson coefficient. \\
		\texttt{c\_bw} & Sets real and imaginary part of the $\Qfour$ Wilson coefficient. \\
		\texttt{c\_tg} & Sets real and imaginary part of the $\Qsix$ Wilson coefficient. \\
		\texttt{c\_bg} & Sets real and imaginary part of the $\Qseven$ Wilson coefficient. \\
		\texttt{lambda} & Scale $\Lambda$, see \cref{subsec:offstop} and ref.~\cite{Neumann:2019kvk}. \\
		\texttt{enable\_lambda4} & Enable contributions of order $1/\Lambda^4$ when set to \texttt{.true.}. \\
		\texttt{disable\_sm} & When set to \texttt{.true.} the pure \SM{} contributions are disabled, and just
		the \SM{}-\EFT{} interference and \EFT{} contributions are calculated. \\
		\texttt{mode\_anomcoup} & When set to \texttt{.true.} at \LO{} one can reproduce results obtained
			without power counting as in the anomalous couplings approach, see \cref{subsec:offstop} and 
			ref.~\cite{Neumann:2019kvk}. \\
               \texttt{nnlo\_enable\_light},
               \texttt{nnlo\_enable\_heavy\_prod},
               \texttt{nnlo\_enable\_heavy\_decay},
               \texttt{nnlo\_enable\_interf\_lxh},
               \texttt{nnlo\_enable\_interf\_lxd},
               \texttt{nnlo\_enable\_interf\_hxd},
               \texttt{nnlo\_fully\_inclusive}&
               At NNLO there are several different contributions from vertex
               corrections on the light-quark line, heavy-quark line in production, and
               heavy-quark line in the top-quark decay. Additionally there are one-loop
               times one-loop interference contributions between all three
               contributions. For a fully inclusive calculation without decay
	       \texttt{nnlo\_fully\_inclusive}  has to
               be set to `.true.` and the decay and decay interference parts have to be
               removed.	 Additionally jet requirements must be lifted.  For further information see
	       \texttt{https://mcfm.fnal.gov/doc/}      \\
    \bottomrule
	\end{longtable}

 

