\midheading*{MCFM - Monte Carlo for FeMtobarn processes}

Authors: John Campbell, Keith Ellis, Tobias Neumann, Ciaran Williams

This is the homepage for the parton-level Monte Carlo program
MCFM. The program calculates cross-sections for various
femtobarn-level processes at hadron-hadron colliders. A number of
processes can be calculated at NNLO order in QCD, while most other
processes are included at NLO order in QCD. The calculation of some
processes can also account for next-to-leading order weak effects. For
more details, look at \href{\mcfmprocs/proclist.html}{list of available processes}
and view the documentation (PDF) with a full list of references. 

\bottomheading*{Documentation}
The full~\href{\mcfmprocs/proclist.html}{list of processes} with links to web-pages
for every process, where examples of input files can be found.
Manuals can be found in Docs/manual.pdf and Docs/cute-mcfm.pdf bundled with MCFM.

\bottomheading*{Download}
\href{https://mcfm.fnal.gov/downloads/MCFM-10.2.2.tar.gz}{MCFM-10.2.2.tar.gz} ( May 19th, 2022, updated November 4th, 2022)

Download and changelog for~\href{https://mcfm.fnal.gov/downloads/earlier_versions.html}{earlier versions of MCFM10 and MCFM9}
and \href{https://mcfm.fnal.gov/downloads/much_earlier_versions.html}{versions prior to MCFM10 and MCFM9}

\bottomheading*{Installation}
The only prerequisites are GNU gcc/g++/gfortran compilers of version 7 or greater and cmake greater than version 3.

In the simplest case the compilation can be done with (e.g. with gfortran)
\begin{verbatim}
tar -zxvf MCFM-10.2.2.tar.gz
cd mcfm/Bin 
cmake -DCMAKE_Fortran_COMPILER=gfortran -DCMAKE_C_COMPILER=gcc -DCMAKE_CXX_COMPILER=g++  ..
make
\end{verbatim}
which uses the bundled LHAPDF. For more options and troubleshooting please see INSTALL and Docs/manual.pdf.


\bottomheading*{New features in MCFM-10}
Since version 10.0 N$^3$LL+NNLO $q_T^2$ resummation for the boson processes $W^+$, $W^-$, $Z$ and $H$ and 
diboson processes $\gamma \gamma$, $Z\gamma$, $ZH$,$W^+H$ and $W^-H$ are included as \href{https://mcfm.fnal.gov/downloads/cute-mcfm.html}{CuTe-MCFM}

\begin{itemize}
\item    C++ interface to tree and one-loop amplitudes as a replacement of OpenLoops and Recola \href{https://arxiv.org/abs/2107.04472}{[2107.04472]}
\item    t-channel single-top-quark production at NNLO \href{https://arxiv.org/abs/2012.01574}{[2012.01574]}, see also \href{https://arxiv.org/abs/2109.10448}{[2109.10448]}
\item    $q_T^2$ resummation for Diphoton production at N$^3$LL$^\prime$+NNLO \href{https://arxiv.org/abs/2107.12478}{[2107.12478]}
\item    Optimized one-loop Higgs+2jet amplitudes with full top-quark mass effects \href{https://arxiv.org/abs/2002.04018}{[2002.04018]}
\item    Off-shell single-top-quark production at NLO including SMEFT contributions \href{https://arxiv.org/abs/1802.02981}{[1802.02981]}
\item    Higgs+jet production at NLO with finite top-quark mass effects (EFT rescaling, $1/m_t^2$) \href{https://arxiv.org/abs/1608.03356}{[1608.03356]}
\item    Electroweak one-loop corrections for $Z$, top-pair and di-jet production \href{https://arxiv.org/abs/1605.08011}{[1605.08011]}
\item    NNLO for $W^+,W^-,Z,H$\href{https://arxiv.org/abs/1605.08011}{[1605.08011]}, $ZH,W^-H,W^+H$ \href{https://arxiv.org/abs/1601.00658}{[1601.00658]},
$\gamma\gamma$\href{https://arxiv.org/abs/1603.02663}{[1603.02663]}
\item    NNLO for $Z\gamma$ \href{https://arxiv.org/abs/1708.02925}{[1708.02925]}, $W\gamma$ \href{https://arxiv.org/abs/2105.00954}{[2105.00954]},
$WW,WZ,WZ,ZZ$ \href{https://arxiv.org/abs/2202.07738}{[2202.07738]}
\item    Use of 0-jettiness or $q_T^2$ as the resolution variable for color-singlet processes \href{https://arxiv.org/abs/2202.07738}{[2202.07738]}
\end{itemize}

\subsubsection*{New features in MCFM-10.2.2}
\begin{itemize}
\item Analytic implementation of $WW$+1jet, $WZ$+1jet and $ZZ$+1jet amplitudes at one loop, also available through the C++ interface.
\item Implementation of $WW,WZ,ZZ$ as well as $W\gamma$ processes at NNLO using both $q_T^2$ and jettiness subtraction, see
\href{https://arxiv.org/abs/2202.07738}{[2202.07738]} and \href{https://arxiv.org/abs/2105.00954}{[2105.00954]}
\item Implementation of $q_T^2$ subtraction for all other color singlet processes.
\item OneLOop~\href{https://arxiv.org/abs/1007.4716}{[1007.4716]} as alternative one-loop provider to QCDLoop.
\item Cleanup of implemention of lepton pair + four parton amplitudes at one loop.
\item 10.2.1: Fixed bug in use of PDFs (introduced in 10.2); fixed error in calculation of top decay width with zerowidth=.false.
\end{itemize}

