\topheading{Versions prior to MCFM-9}
\label{priorversions}
\midheading{MCFM-8}
\begin{itemize}
\item \href{https://mcfm.fnal.gov/downloads/MCFM-8.3.tar.gz}{MCFM-8.3.tar.gz} (released April 4th, 2019), v8.3 manual (PDF)

\begin{itemize}
\item    New processes for off-shell SM and SMEFT single-top-quark production
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-8.2.tar.gz}{MCFM-8.2.tar.gz} (released February 8th, 2018)

\begin{itemize}
\item    Implementation of high-pt treatment of mass effects in H+jet process.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-8.1.tar.gz}{MCFM-8.1.tar.gz} (released December 19th, 2017)

\begin{itemize}
\item    Electroweak one-loop corrections for Z, top-pair and di-jet production.
\item    Z+photon process at NNLO including anomalous couplings.
\item    H+2 jet process with a finite top-quark mass (LO) and H+jet with finite top-quark mass effects (NLO)
\item    Support for boosted (as opposed to hadronic) definition of jettiness, which is now also used as default.
\item    Support for pt and rapidity ranges for most cuts in the input file.
\item    Native implementation of two PDF sets containing photons: mrstqed and CT14qed.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-8.0.tar.gz}{MCFM-8.0.tar.gz} (released May 25th, 2016; updated June 2nd to fix MMHT implementation)

\begin{itemize}
\item    Introduced NNLO capability for color-singlet processes.
\item    Overall improvement in speed.
\end{itemize}
\end{itemize}

\midheading{MCFM-7}
\begin{itemize}
\item \href{https://mcfm.fnal.gov/downloads/MCFM-7.0.1.tar.gz}{MCFM-7.0.1.tar.gz} (released October 29th, 2015)

\begin{itemize}
\item    Fixed error in real calculation for some versions of gcc 4.x.
\item   Updated output to support ROOT6.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-7.0.tar.gz}{MCFM-7.0.tar.gz} (released March 21st, 2015; updated June 11 for gfortran 4.9)

\begin{itemize}
\item    Code compiles with the OpenMP flag to automatically exploit all available threads.
\item    Added four-photon process at NLO.
\item    Inclusion of vector boson fusion/vector boson scattering processes at LO.
\item    After Higgs discovery, added s-channel Higgs diagrams to the gg->VV processes.
\end{itemize}
\end{itemize}
\midheading{MCFM-6}
\begin{itemize}
\item \href{https://mcfm.fnal.gov/downloads/MCFM-6.8.tar.gz}{MCFM-6.8.tar.gz}

\begin{itemize}
\item    Added process for diphoton+jet production at NLO.
\item    Added identical-particle interference effects for 4-lepton production and effect of WW/ZZ interference for 2-lepton, 2-neutrino production.
\item    Added additional decay modes for WW and ZZ processes.
\item    Fixed bug in triphoton process at NLO.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-6.7.tar.gz}{MCFM-6.7.tar.gz} (December 6th, 2013)

\begin{itemize}
\item    New implementation of $gg \to ZZ$ box contribution including massive loops.
\item    Added processes for triphoton production at NLO, 1-loop Higgs pair production.
\item    Fixed errors reported in native histograms and improved PDF uncertainty output. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-6.6.tar.gz}{MCFM-6.6.tar.gz} (April 1st, 2013)

\begin{itemize}
\item    Implementation of single top tH and tZ processes.
\item    Implementation of dark matter mono-jet and mono-photon processes.
\item    Inclusion of TensorReduction library for one-loop integrals. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/MCFM-6.5.tar.gz}{MCFM-6.5.tar.gz} (March 5th, 2013)

\item \href{https://mcfm.fnal.gov/downloads/mcfm-6.4.tar.gz}{mcfm-6.4.tar.gz} (December 22nd, 2012)

\begin{itemize}
\item    Corrected bug in implementation of one-loop amplitudes for H+2q+2g processes.
\item    Enabled effect of removebr for process 307.
\item    Fixed the implementation of a dynamic scale for single top + b processes.
\item   Added a new scale choice for top production ($m_{345}^{2}+p_{T}(345)^{2}$).
\item    Improved numerical stability in calculation of virtual contribution to process 201 and in calculation of real corrections to processes 180-187. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-6.3.tar.gz}{mcfm-6.3.tar.gz} (August 10th, 2012)

\begin{itemize}
\item    Added processes giving the radiation in the hadronic decay of the W+W- process.
\item    Added processes giving the gg to H to WW process with radiation in the hadronic decay of the W.
\item    Added processes giving the production and decay of t tbar W+/- including radiation in the semi-leptonic decay of the top and the anti-top.
\item    Added processes giving the $H \to Z\gamma$ in the gluon fusion production process.
\item    Added processes describing production of $Z+\gamma+\gamma$ and $Z+\gamma$+jet at NLO. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-6.2.tar.gz}{mcfm-6.2.tar.gz} (April 10th, 2012)

\begin{itemize}
\item    Added processes that give results for the t-channel single top process in the four-flavour scheme with top decay;
\item    Added process for Higgs + 2 jets, with Higgs decaying to $\gamma\gamma$;
\item    Added processes for Wb production from charm quarks;
\item    Added LO processes for Higgs + 3 jets with Higgs decaying to WW or ZZ;
\item    Added LO process for identical fermions in ZZ decay;
\item    corrected small bugs. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-6.1.tar.gz}{mcfm-6.1.tar.gz} (October 19th, 2011)

\begin{itemize}
\item    inclusion of massive (t,b) loops in $gg \to WW$ diagrams;
\item    new process for computing effect of interference with Higgs diagrams for $gg \to WW$;
\item    inclusion of direct photon production including fragmentation;
\item    anomalous couplings for $W\gamma$ and $Z\gamma$ production;
\item    improved interface and output, corrected small bugs. 
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-6.0.tar.gz}{mcfm-6.0.tar.gz} (May 2nd, 2011)

\begin{itemize}
\item    NLO results for Wbb production including heavy quark mass effects;
\item   inclusion of $W\gamma$, $Z\gamma$ and $\gamma\gamma$ processes with fragmentation;
\item    gluon-initiated contributions to diboson processes;
\item    small correction to Z+2 jet process and other bug fixes. 
\end{itemize}

\end{itemize}
\midheading{MCFM-5 and before}
\begin{itemize}
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.8.tar.gz}{mcfm-5.8.tar.gz} (April 9th, 2010)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.7.tar.gz}{mcfm-5.7.tar.gz} (January 22nd, 2010)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.6.tar.gz}{mcfm-5.6.tar.gz} (July 31st, 2009)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.5.tar.gz}{mcfm-5.5.tar.gz} (June 5th, 2009)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.4.tar.gz}{mcfm-5.4.tar.gz} (March 12th, 2009)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.3.tar.gz}{mcfm-5.3.tar.gz} (October 21st, 2008)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.2.tar.gz}{mcfm-5.2.tar.gz} (July 12th, 2007)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.1.tar.gz}{mcfm-5.1.tar.gz} (June 1st, 2006)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-5.0.tar.gz}{mcfm-5.0.tar.gz} (April 25th, 2006)
\item \href{https://mcfm.fnal.gov/downloads/mcfm-4.1.tar.gz}{mcfm-4.1.tar.gz} (January 17th, 2005)

\item \href{https://mcfm.fnal.gov/downloads/mcfm-4.0.tar.gz}{mcfm-4.0.tar.gz} (October 15th, 2004)
\begin{itemize}
\item Major revision of the code, which now includes single top processes.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.5.tar.gz}{mcfm-3.4.5.tar.gz} (December 23rd, 2003)
\begin{itemize}
\item Minor update, addition of LO WW production with no polarization info, process 64.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.4.tar.gz}{mcfm-3.4.4.tar.gz} (September 3rd, 2003)
\begin{itemize}
\item Minor update, mostly cosmetic changes.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.3.tar.gz}{mcfm-3.4.3.tar.gz} (July 2nd, 2003)
\begin{itemize}
\item Bug fixes for input files using the 'tota' option at NLO.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.2.tar.gz}{mcfm-3.4.2.tar.gz} (June 6th, 2003)
\begin{itemize}
\item Further minor improvements over version 3.4.1.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.1.tar.gz}{mcfm-3.4.1.tar.gz} (May 29th, 2003)
\begin{itemize}
\item Minor improvements over version 3.4.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.4.tar.gz}{mcfm-3.4.tar.gz} (April 24th, 2003)
\begin{itemize}
\item Version 3.4 contains a number of new Higgs production processes at next-to-leading order.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-3.2.tar.gz}{mcfm-3.2.tar.gz} (October 1st, 2002)

\item \href{https://mcfm.fnal.gov/downloads/mcfm-2.1.tar.gz}{mcfm-2.1.tar.gz} (December 14th, 2001)
\begin{itemize}
\item An old version, preserved for historical value only.
\end{itemize}

\item \href{https://mcfm.fnal.gov/downloads/mcfm-1.0.tar.gz}{mcfm-1.0.tar.gz}
\begin{itemize}
\item An old version, preserved for historical value only.
\end{itemize}
\end{itemize}
