\midheading{$t\bar{t}$ production with one hadronic decay, processes 146--151}

This process is calculable at leading LO and next-to-leading order NLO.
These processes describe the hadronic production of a pair of top
quarks, with one quark decaying hadronically and one quark decaying
semi-leptonically.  For processes {\tt 146--148}, the top quark decays
semi-leptonically whereas the anti-top quark decays hadronically.  For
processes {\tt 149--151}, the top quark decays hadronically whereas the
anti-top quark decays semi-leptonically.  The base processes for
physics are process {\tt 146} and {\tt 149} which include
radiative corrections in both production and decay.  Switching {\tt zerowidth} from
{\tt .true.} to {\tt .false.} only affects the $W$ bosons from the top
quark decay, because our method of including spin correlations
requires the top quark to be on shell.
When one wishes to calculate observables related to the decay of the top
quark, {\tt removebr} should be false in processes {\tt 146} and {\tt 149}.
The LO calculation proceeds as normal. At NLO, there are two options:
\begin{itemize}
\item {\tt part=virt, real} or {\tt tota} : final state radiation is included
in the production stage only
\item {\tt part = todk} : radiation is included in the decay of the top
quark also and the final result corresponds to the sum of real and virtual
diagrams.
Note that these runs automatically perform an extra integration, so
will take a little longer.
\end{itemize}


Processes {\tt 147} and {\tt 150} include only the radiative
corrections in the decay of the top quark without including
the radiative corrections in the hadronic decay of the $W$-boson.
Because of the method that we have used to include the radiation in the decays,
the inclusion of the corrections in this stage of the decay does not change the
total cross section.
Process {\tt 148} ({\tt 151}) includes only the radiative corrections
in the hadronic decay of the $W$-boson coming from the anti-top (top).
The inclusion of the corrections in this stage of the decay increases the
partial width by the normal $\alpha_s/\pi$ factor.
