\midheading{$t$-channel single top with an explicit $b$-quark, processes 231--240}
\label{subsec:stopb}

These represent calculations of the $t$-channel single top~({\tt 231}) and anti-top~({\tt 231})
processes in a scheme with four flavours of quark in the proton, so that $b$-quarks are not present in the proton.
The $b$-quark is instead explicitly included in the final state.
For more details on this calculation, please see Ref.~\cite{Campbell:2009ss}.

Processes {\tt 232} and {\tt 236} represent $t$-channel single top production in association
with a further jet and may be calculated at LO only.

Processes {\tt 233} and {\tt 238} are the complete four-flavour scheme $t$-channel single top production processes.
These are therefore the processes that should be used for most physics applications.
When one wishes to calculate observables related to the decay of the top
quark, {\tt removebr} should be false in processes {\tt 233} and {\tt 236}.
The LO calculation proceeds as normal. At NLO, there are two options:
\begin{itemize}
\item {\tt part=virt, real} or {\tt tota} : final state radiation is included
in the production stage only
\item {\tt part = todk} : radiation is included in the decay of the top
quark also and the final result corresponds to the sum of real and virtual
diagrams.
Note that these runs automatically perform an extra integration, so
will take a little longer.
\end{itemize}


Processes {\tt 234} and {\tt 239} give the extra contribution due to radiation
in top decay. These processes are mainly of theoretical interest.

Processes {\tt 235} and {\tt 240} are the leading order single top processes with an
extra radiated parton. These processes do not includes jets produced in the decay process.
