\midheading{$W+t{\bar t}$ processes 500--516}
\label{subsec:wttdecay}

These processes represent the production of a $W^\pm$ boson which subsequently
decays leptonically, in association with a $t{\bar t}$ pair. In all except processes
{\tt 500} and {\tt 510} the decays of the top and anti-top quark are included.
Processes {\tt 501,502} and {\tt 511,512} refer to the semileptonic decay of the top and antitop quarks,
with the latter process in each pair giving the radiation in the decay of the top and antitop.
Process {\tt 503} ({\tt 513}) refers to the semileptonic decay of the top (antitop)
and the hadronic decay of the antitop (top). Processes {\tt 506}({\tt 516}) gives the semileptonic
decay of the antitop(top) and the hadronic decay of the top(antitop).  Processes {\tt 506}({\tt 516})
do not give same sign lepton events, so they may be of less phenomenological importance. For this reason
we have not yet included radiation in the decay for these processes.

For processes {\tt 503}, {\tt 506}, {\tt 513}
and {\tt 516} the default behaviour is that the hadronic decay products
are clustered into jets using the supplied jet
algorithm parameters, but no cut is applied on the number of jets.
This behaviour can be altered by changing the value of the
variable {\tt notag} in the file {\tt src/User/setnotag.f}.

The top quarks are always
produced on-shell, which is a necessity for a gauge invariant result
from this limited set of diagrams, but all spin correlations are included.
Switching {\tt zerowidth} from {\tt .true.} to {\tt .false.} only affects
the $W$ bosons (both the directly produced one and from the top quark decay).
Processes {\tt 501} and {\tt 511} may be run at NLO with the option {\tt todk},
including radiation in the decay of the top quark, see section \ref{subsec:ttbar}.
