\midheading{$Z+2$~jets production, processes 44, 46}
\label{subsec:z2jets}

These processes represents the production of a $Z$ boson and $2$ jets,
including also the effect of a virtual photon ({\tt nproc=44} only). The $Z/\gamma^*$ decays
to an $e^+ e^-$ pair ({\tt nproc=44}) or into three species of neutrino ({\tt nproc=46}).
Virtual amplitudes are taken from ref.~\cite{Bern:1997sc}.
For more details on this calculation, please see
Refs.~\cite{Campbell:2002tg,Campbell:2003hd}.

The calculation may be performed up to NLO.
For $Z+2$~jet production
the next-to-leading order matrix elements are
particularly complex and so they have been divided into two groups.
The division is according to the lowest order diagrams from which they
originate:
\begin{enumerate}
\item Diagrams involving two external quark lines and two external gluons,
the ``{\tt Gflag}'' contribution. The real diagrams in this case thus
involve three external gluons.

\item Diagrams where all four external lines are quarks,
the ``{\tt Qflag}'' contribution. The real diagrams in this case
involve only one gluon.
\end{enumerate}

By specifying {\tt Gflag} and {\tt Qflag} in the file {\tt input.ini} one may
select one of these options at a time. The full result may be obtained
by straightforward addition of the two individual pieces, with no
meaning attached to either piece separately.
The default is that both of these are set to {\tt .true.} simultaneously.

When {\tt removebr} is true, the $Z$ boson does not decay.
